figures and calculations for global fisheries management

### 2019-01-11 documents/figs-and-calcs.Rmd
populated regression portion of figs-calc document

---
title: "figures and calculations for global fisheries management"
output: html_notebook
---

@@

>>>>

---
title: "figures and calculations for global fisheries management"
output:
  pdf_document: default
  html_notebook: default
---

@@

GDP data source: UN website
Regular ISSCAAP Categories
```{r}

projection_data <- readRDS(here("data","projection_data.rds")) %>% 
  filter(Scenario == "Historic")

gdp_all <- read_excel(here("data","un_gdp_2016.xls"))

gdp <- gdp_all %>%
  select(Country, gdp_center) %>%
  filter( gdp_center != "NA")

join <- left_join(projection_data, gdp, by = "Country")

join$SpeciesCat <- factor(join$SpeciesCat)

glm <- glm(formula = CatchShare ~ gdp_center + SpeciesCat, family = "binomial", data = join)
glm

summary(glm)

Broader ISSCAAP Categories
22-24 = diadromous fishes = 2
31-35, 37 = marine fishes = 3
42-45,47 = crustaceans = 4
52-58 = molluscs = 5
74,76,77 = miscellaneous aquatic animals = 7

projection_data <- readRDS(here("data","projection_data.rds")) %>% 
  filter(Scenario == "Historic")

projection_data_mutate <- projection_data  %>%
  mutate(MainCat = case_when(
    SpeciesCat == 22 | SpeciesCat == 23 | SpeciesCat == 24 ~ "2",
    SpeciesCat == 31 | SpeciesCat == 32 | SpeciesCat == 33 | SpeciesCat == 34 | SpeciesCat     == 35 | SpeciesCat == 37 ~ "3",
    SpeciesCat == 42 | SpeciesCat == 43 | SpeciesCat == 44 | SpeciesCat == 45 | SpeciesCat      == 47 ~ "4",
    SpeciesCat == 52 | SpeciesCat == 53 | SpeciesCat ==54 |  SpeciesCat == 55 | SpeciesCat     == 56 | SpeciesCat == 57 | SpeciesCat == 58 ~ "5",
    SpeciesCat == 74 | SpeciesCat == 76 | SpeciesCat == 77 ~ "7"
  ))

gdp_all <- read_excel(here("data","un_gdp_2016.xls"))

gdp <- gdp_all %>%
  select(Country, gdp_center) %>%
  filter( gdp_center != "NA")

join_mutate <- left_join(projection_data_mutate, gdp, by = "Country")

join_mutate$MainCat <- factor(join_mutate$MainCat)

glm_broad <- glm(formula = CatchShare ~ gdp_center + MainCat, family = "binomial", data = join_mutate)
glm_broad

summary(glm_broad)
